Concurrent Programming in Harmony

### 2021-12-30 book/paper.tex
Latest

>>>>

\begin{figure}
\begin{code}
<{:input:../code/RWcheat.hny}>
\end{code}
\caption{\harmonylink{code/RWcheat.hny} "Cheating" reader/writer lock}
\label{fig:rwcheat}
\end{figure}

\begin{figure}
\begin{code}
<{:input:../code/RWbtest.hny}>
\end{code}
\caption{\harmonylink{code/RWbtest.hny} A behavioral test of reader/writer locks}
\label{fig:rwbtest}
\end{figure}

A problem with this test is that it does not find a problem
with an implementation like the one in \autoref{fig:rwcheat}.
This implementation implements a reader/writer lock as an ordinary
lock, and thus lets only one thread in the critical section at a time.
In some sense, the implementation is correct because it satisfies
the requirements, but it is clearly not a desirable implementation.
For a case like this one, it is better to compare behaviors between
the specification and the implementation.

\autoref{fig:rwbtest} is the same test as \autoref{fig:rwtest} but
prints identifying information before and every lock operation.
Now we can compare behaviors as follows:

\begin{code}
\begin{verbatim}
$ harmony -o rw.hfa -o rwspec.png -cNOPS=2 code/RWbtest.hny
$ harmony -B rw.hfa -o rwimpl.png -cNOPS=2 -m RW=RWcheat code/RWbtest.hny
\end{verbatim}
\end{code}

The second command will print a warning that there are behaviors in the
specification that are not achieved by the implementation.
We set <{NOPS}> to 2 to make the behaviors relatively small and easier
to compare.
It is now possible to compare the outputs in \texttt{rwspec.png}
and \texttt{rwimpl.png} and see what behaviors are allowed by the
specification that are not allowed by the implementation.
(Harmony does not yet have a mechanism to do this automatically.)
